Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-04 article.tex
some wording precision

\section{Method}

@@

% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
In our last submission in hope to improve performance, some causal information
(directivity of the links) were added by stacking the partial correlation score
matrix with an pairwise activation heuristics. This method computes an
activation score $z_{ij}$ based the variation of fluorescence signal of a neuron
$j$ due to a neuron $i$ over all timesteps:
\[
z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
\]
where $f_1$ and $f_2$ are parameters of the method and $I$ is the
indicator function.

% Introduce filtering

>>>>

\section{Network inference methodology}

@@

% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
In our last submission in hope to improve performance, some causal information
(directivity of the links) were added by stacking the partial correlation score
matrix with an pairwise activation heuristics. This method computes an anti-symmetric
activation score $z_{ij}$ based the variation of fluorescence signal of a neuron
$j$ due to a neuron $i$ over all timesteps:
\[
z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
\]
where $f_1$ and $f_2$ are parameters of the method and $I$ is the
indicator function.

% Introduce filtering
\section{Signal filtering methodology}
